Turchin's method of statistical regularization

### 2018-02-27 AYSS-2017/article/ayss2017-Zeleniy.tex

Consider eq. ~\ref{eq-01} in operator form:
\begin{equation}
	\label{eq-02}
    \hat{K}\varphi = f.
\end{equation}

@@

In eq. ~\ref{eq-smoothness} one can use not only smoothness operator, but also different or even multiple different conditions: 
\begin{equation*}
    P_{\alpha\beta}(\varphi) \sim  \det \left|\alpha\Omega_1 +\beta\Omega_2\right|\exp\left(-\frac{1}{2} (\vec{\varphi},(\alpha\Omega_1 + \beta\Omega_2)\vec{\varphi})\right)
\end{equation*}

@@

In order to find numerical solution, one need to go from continuous functions in eq. ~\ref{eq-02} to discreet matrix form:
\begin{equation}\label{eq:algebr}
	\begin{gathered}
      \varphi(x) = \sum \limits_n \varphi_n T_n(x),\\
      K_{mn} = (\hat{K}T_n(x))(y_m),\\
      \Omega_{ij} = \int\limits_a^b \left(\frac{d^pT_i(x)}{dx}\right)\left(\frac{d^pT_j(x)}{dx}\right)dx,\\
      D[\varphi(x)] = D[\sum \limits_n \varphi_n T_n(x)] = \sum\limits_{i,j} \varphi_i\varphi_j cov(T_i(x), T_j(x)),\\
      \vec{f} = K\vec{\varphi},
    \end{gathered}
\end{equation}
where $T_n(x)$ - some basis in function space. For example, cubic spline, Fourier series and Legendre polynomials.

>>>>

Consider eq.~\ref{eq-01} in operator form:
\begin{equation}
	\label{eq-02}
    \hat{K}\varphi = f.
\end{equation}

@@

In eq.~\ref{eq-smoothness} one can use not only smoothness operator, but also different or even multiple different conditions: 
\begin{equation*}
    P_{\alpha\beta}(\varphi) \sim  \det \left|\alpha\Omega_1 +\beta\Omega_2\right|\exp\left(-\frac{1}{2} (\vec{\varphi},(\alpha\Omega_1 + \beta\Omega_2)\vec{\varphi})\right)
\end{equation*}

@@

In order to find numerical solution, one need to go from continuous functions in eq.~\ref{eq-02} to discrete matrix form:
\begin{equation}\label{eq:algebr}
	\begin{gathered}
      \varphi(x) = \sum \limits_n \varphi_n T_n(x),\\
      K_{mn} = (\hat{K}T_n(x))(y_m),\\
      \Omega_{ij} = \int\limits_a^b \left(\frac{d^pT_i(x)}{dx}\right)\left(\frac{d^pT_j(x)}{dx}\right)dx,\\
      D[\varphi(x)] = D[\sum \limits_n \varphi_n T_n(x)] = \sum\limits_{i,j} \varphi_i\varphi_j cov(T_i(x), T_j(x)),\\
      \vec{f} = K\vec{\varphi},
    \end{gathered}
\end{equation}
where $T_n(x)$ - some basis in function space. For example, cubic spline, Fourier series and Legendre polynomials.
